### 2018-05-30 Physics Notes/Paper 1/Paper 1.tex
Paper 1 Notes

\documentclass[12pt]{article}
\usepackage{../../format}
\lhead{A Level Physics}
\setcounter{secnumdepth}{5}
\usepackage[compat=1.1.0]{tikz-feynman}

%REMINDER: This needs to be compiled with LuaLaTeX to work

@@

>>>>

\documentclass[12pt]{article}
\usepackage{../../format}
\lhead{A Level Physics}
\setcounter{secnumdepth}{5}
\usepackage[english]{babel}

\makeatletter
\renewcommand{\paragraph}{\@startsection{paragraph}{4}{0ex}%
    {-3.25ex plus -1ex minus -0.2ex}%
    {1.5ex plus 0.2ex}%
    {\normalfont\normalsize\bfseries}}
\makeatother

@@

\paragraph{Kaons and pions}
Kaons (K mesons) decay into Pions($\pi$ mesons), they decay by the weak interaction, so strangeness need not be conserved
$$K^+\rightarrow \mu^++\nu_\mu$$
$$K^+\rightarrow \pi^++\pi^0$$
$$K^-\rightarrow \mu^-+\overline{\nu_\mu}$$
$$K^-\rightarrow \pi^-+\pi^0$$
$$K^-\rightarrow \pi^0+\mu^-+\overline{\nu_\mu}$$
\paragraph{Leptons}
Lepton number is conserved in an interaction, muons decay into electrons
$$\mu^-\rightarrow e^-+\overline{\nu_e}+\nu_\mu$$
$$\mu^+\rightarrow e^++\nu_e+\overline{\nu_\mu}$$
\paragraph{Strange particles}
Strange particles are produced through the strong interaction and decay through the weak interaction, this is because strangeness is conserved during the strong interaction, but not during the weak interaction.
\subsubsection{Quarks and antiquarks}
Differences between quarks and antiquarks
\item Opposite strangeness
\item Opposite charge
\item Opposite strangeness
\paragraph{Quark compositions}
\item Proton -UUD
\item Neutron - DUD
\item Pion - Not strange, sign indicates charge
\item Kaon - Strange, sign indicates charge
\subsubsection{Applications of conservation laws}
Changes of quark nature
\item $\beta^-$, down $\rightarrow$ up
\item $\beta^+$, up $\rightarrow$ down
\includegraphics[width=10cm]{quark_beta.png}
In all interactions, energy and momentum must be conserved
\subsection{Electromagnetic radiation and quantum phenomena}
\subsubsection{The photoelectric effect}
\textbf{Photoelectric effect} - The emission of electrons from a metal surface when the surface is illuminated by a light of frequency greater than a minimum value known as the threshold frequency
\paragraph{Threshold frequency}
Because the energy of a photon is proportional to its frequency ($E=hf$), a minimum frequency must be reached so that the electrons have sufficient energy to escape the surface
\paragraph{Work function and stopping potential}
\textbf{Work function} - The minimum amount of energy needed by an electron to escape from a metal surface\\
\textbf{Stopping potential} - The potential difference required to stop an electron
\paragraph{The photoelectric equation}
$$hf=\phi+E_{K(Max)}$$
$hf$ is the energy of the incident photon\\
$\phi$ is the work function\\
$E_{K(max)}$ is the maximum kinetic energy\\
Electrons emitted will have a range of kinetic energies, depending how much work is done to escape the metal
\begin{tikzpicture}
\begin{axis}[axis lines=middle,scale=0.8,ylabel = KE,xlabel=Frequency,ylabel style={rotate=90,anchor=south},xlabel style={anchor=south},xmin=0,xmax=7,ymin=-5,ymax=7,xtick={2},xticklabels={$F_0$},ytick={-2},yticklabels={$-\Phi$}
]
\addplot[color=black,domain=0:7]{x-2};
\end{axis}
\end{tikzpicture}\\
The gradient of the line is Planck's constant
\subsubsection{Collisions of electrons with atoms}
\paragraph{Ionisation and excitation}
\textbf{Ion} - A charged atom\\
\textbf{Ionisation} - The process of creating ions\\
\textbf{Excitation} - The process in which an atom absorbs energy without becoming ionised as a result of an electron inside an atom moving from an inner shell to an outer shell
\paragraph{•}
